\documentclass[]{twentysecondcv}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
 
\begin{document}

%%%%%%%%%%%%%%%%%
%%PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%
%%PERSONAL INFO%%%
%%%%%%%%%%%%%%%%

\profilepic{picture} %path of profile pic
\cvname{Alexander Jansing} %your name
\cvjobtitle{Data / Software Engineer}%your actual job position
\cvdate{28 April 1989}%date of birth
\cvaddress{Liverpool, NY 13088}%address
\cvnumberphone{(315) 601-8991}%telphone number
\cvmail{alexander.jansing@gmail.com}%e-mail
\cvsite{apjansing.github.io}%personal site


\aboutme{
Air Force and Air National Guard veteran with a Bachelor of Science in Applied Mathematics and a planned graudation date of May 2019 to finish a Master of Science in Computer Science. Attends local Meetups and hackathons to further knowledge and get a better feel for professional environments outside of the defense industry.
}%About me section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill bar section, each skill must have a value between 0 an 6 (float)%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skills{{Bash/3.7}, {HTML, CSS, Javascript/4}, {Scala, MATLAB/5.6}, {Java, Python/5.8}}
\databases{{OrientDB, TitanDB, Spark GraphX/2.5}, {MongoDB, Postgres/2.5}, {Hadoop, Accumulo/2.5}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill text section, each skill must have a value between 0 an 6%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skillstext{{Bash/3.7}, {HTML/4}, {Java/5.8}}

\makeprofile
%%%%%%%%%%%%%%%%%%%%
%%END PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%BODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%SIMPLE SECTION%%%%%%
%%%%%%%%%%%%%%%%%%%%
\section{interests}
Free time is spent with friends, at hackathons, writing code, or unwinding with a good game or book.

\section{education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%TWENTY LIST ITEMS%%%%%%%%%%%%%%
%%    Four arguments: date; title; where; description %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{twenty}
  \twentyitem
    {2015-2019}
    {M.S. Computer and Information Sciences}
    {SUNY Polytechnic}
    {Focus in Software Engineering and Mathematics \\
    \hspace*{-4em} Relevant courses:
      $$
      \begin{array}{ccc}
        \textmd{Quantum Computing} & \textmd{AI Topic: Data Science} & \textmd{Machine Learning} \\
        \textmd{Formal Methods} & \textmd{Big Data Platforms} & \textmd{Parallel Computing} \\
         & \textmd{Numerical Diff Equations} & 
      \end{array}
      $$}
  \twentyitem
    {2012-2015}
    {B.S. Applied Mathematics}
    {SUNY Oswego}
    {Cognate in Computer Science}
\end{twenty}


\section{experience}

\begin{twenty}
  \twentyitem
  {2018--\footnotesize Present}
  {Software Engineer, Mid -- Computer Science}
  {Booz Allen Hamilton}
  {Working as an Implementation Specialist on the Swift project. Using Concourse, Sonarqube, Docker, and Bash scripts to create CI/CD pipelines that can be applied to arbitrary projects with minimal adaptation.}
  \twentyitem
  {2018--2018}
  {Software Engineer, Asc}
  {Lockheed Martin}
  {Worked on a variety of projects involving signal processing. Developed analytics for Noise Reduction and identification of Modulation techniques using methods like KMeans and DenseNet.}
  \twentyitem
  {2016--2018}
  {Data Scientist, Junior -- Computer Science}
  {Booz Allen Hamilton}
  {Worked on the AFRL Active Insights project that was demoed at GeoINT2017 and will be demoed at GeoINT2018. Work focused on ETL, designing a data lake, and provenance tracking.}
  \twentyitem
  {2015--2016}{Graduate Assistant}{SUNY Polytechnic}{Graded homework, held office hours, and designed grading schemes for Finite Mathematics.}

\end{twenty}

\section{awards}
  \begin{twenty}
    \twentyitem
    {2018}
    {Open House Planner} % Project Title
    {Hack Upstate XII} % Prize - Where
    {\href{https://medium.com/@hackupstate/hack-upstate-xii-the-results-are-in-e5be2f4edcc0}{Grand Prize and Best Use of Esri Technology}\\
    A project that was inspired by a real-world problem.\\
    ``What if two houses are significantly far apart, open at similar times, and there are other houses in each of their respective neighborhoods that open at different times? Is there a way I can plan my day of house hunting so that I can attend all of the open houses?"} % Reason
    \twentyitem
      {2018}
      {Move Helper} % Project Title
      {Hack Mohawk Valley} % Prize - Where
      {\href{https://medium.com/@hackupstate/hack-mohawk-valley-the-results-are-in-4dff78924a61\#9a90}{Best Use or Open Data}} % Reason
    \twentyitem
    {2018}
      {Buffalo Crime Data} % Project Title
      {Hack Upstate XI} % Prize - Where
      {\href{https://medium.com/@hackupstate/hack-upstate-xi-the-results-are-in-5ee7973f25a\#ffa5}{Buffalo Civic Innovation Challenge}\\
      } % Reason
  \end{twenty}

\newpage
\makeprofile
\section{Presentations}
\begin{twenty}
  \twentyitem
  {2016}
  {An Overview and Brief Tutorial of Niagara Files}
  {Booz Allen Hamilton Tech Talks} % Prize - Where
  {Booz Allen Hamilton's internal webcast and conference line.
  Niagara Files (Nifi) is a digraph ETL program that provides a web-based UI, loss tolerance, data provenance, and the ability to create custom processors using a Maven archetype. Covered what a FlowFile is and some of the most important concepts of Nifi that are needed to understand before working with Nifi.}
  
  \twentyitem
  {2015}
  {Lie Algebras}
  {SUNY Oswego Mathematics Department}
  {
  Lie algebras have two special operators, the Lie bracket and the inner product and they both have special characteristics that impose algebraic and geometry restrictions on the spaces they apply to. We looked at how they interact, and wrote programs in \textsc{Sage (Python)} that generate general forms of the matrix representations of these interactions.}
\end{twenty}

\section{Computer skills}
\begin{twenty}
  \twentyitemshort
  {Languages}{Java, Python, Scala, Matlab, R, Groovy, Bash, \LaTeX, Javascript, Bash, HTML, CSS}
  \twentyitemshort {Databases}{Accumulo, OrientDB, TitanDB, MongoDB, Postgres, Hadoop} 
  \twentyitemshort {Technologies}{Git, Jira, Confluence, Nifi, Apex, Spark, AWS, Maven, Docker, Docker Compose, Concourse}
  \twentyitemshort {Systems}{Linux (CentOS and Ubuntu), Mac, Windows}
\end{twenty}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%TWENTY LIST SHORTITEMS%%%%%%%%%%%%%%
%%% Two arguments: date; title/description %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{publications}

% \begin{twentyshort}
%   \twentyitemshort
%     {1865}
%     {Chapter One, Down the Rabbit Hole.}
%   \twentyitemshort
%     {1865}
%     {Chapter Two, The Pool of Tears.}
%   \twentyitemshort
%     {1865}
%     {Chapter Three,  The Caucus Race and a Long Tale.}
%   \twentyitemshort
%     {1865}
%     {Chapter Four,  The Rabbit Sends a Little Bill.}
%   \twentyitemshort
%     {1865}
%     {Chapter Five,  Advice from a Caterpillar.}
% \end{twentyshort}



% \section{awards}

% \begin{twentyshort}
%   \twentyitemshort
%     {1987}
%     {All-Time Best Fantasy Novel.}
%   \twentyitemshort
%     {1998}
%     {All-Time Best Fantasy Novel before 1990.}
% \end{twentyshort}

% \section{other information}
% Alice approaches Wonderland as an anthropologist, but maintains a strong sense of noblesse oblige that comes with her class status. She has confidence in her social position, education, and the Victorian virtue of good manners. Alice has a feeling of entitlement, particularly when comparing herself to Mabel, whom she declares has a “poky little house,” and no toys. Additionally, she flaunts her limited information base with anyone who will listen and becomes increasingly obsessed with the importance of good manners as she deals with the rude creatures of Wonderland. Alice maintains a superior attitude and behaves with solicitous indulgence toward those she believes are less privileged.

%%%%%%%%%%%%%%%%%%%%
%%%%%ENDBODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{document} 